A Comparison of Parallel Graph Processing Implementations

### 2017-05-15 papers/publication/paper-pollard.tex
related edits

\section{Related Work}\label{sec:relatedwork}
Most performance analysis of graph processing systems come from the empirical results of each new library designer's publications. For example, GraphMat~\cite{Sundaram:2015:GraphMat}, PowerGraph~\cite{Gonzalez:2012:Powergraph}, and GraphBIG~\cite{Nai:2015:Graphbig} present a comparison of performance between their system and a selection of other software packages and in general any new approach will compare itself to existing implementations. These performance results are inherently biased because the authors will know their own package better than the competition and as such are aware of more optimizations.

@@

However, perusal of the log files reveals a different story. The listing contained below Table~\ref{tab:graphalytics-realworld} is the output from GraphMat itself. Graphalytics reports a 3.8 second runtime but 0.94 seconds of which GraphMat is simply reading the input file from disk. However, the GraphBIG timing (3.0 seconds) does not include the time to read the dota-league file. \textbf{If the time to read in the text file was computed correctly, GraphMat would be faster than GraphBIG.} To call this a fair comparison is dubious at best when phases of execution are omitted.

>>>>

\section{Related Work}\label{sec:relatedwork}
Most performance analysis of graph processing systems come from the empirical results of each new library designer's publications. For example, GraphMat~\cite{Sundaram:2015:GraphMat}, PowerGraph~\cite{Gonzalez:2012:Powergraph}, and GraphBIG~\cite{Nai:2015:Graphbig} present a comparison of performance between their system and a selection of other software packages and in general any new approach will compare itself to existing implementations. These performance results are inherently biased because the authors typically know their own package better than the competition and as such are aware of more optimizations.

@@

However, perusal of the log files reveals a different story. The listing shown below Table~\ref{tab:graphalytics-realworld} is the output from GraphMat itself. Graphalytics reports a 3.8 second runtime but 0.94 seconds of which GraphMat is simply reading the input file from disk. However, the GraphBIG timing (3.0 seconds) does not include the time to read the dota-league file. \textbf{If the time to read in the text file was computed correctly, GraphMat would be faster than GraphBIG.} To call this a fair comparison is dubious at best when certain phases of execution are omitted for some packages but not others.
